---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(str = strOptions(strict.width = "cut"))
```

# gleif

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/m-muecke/gleif/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/m-muecke/gleif/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/gleif)](https://CRAN.R-project.org/package=gleif)
<!-- badges: end -->

gleif is a minimal R client for the [gleif](https://www.gleif.org) API.
A major challenge when dealing with financial data is the mapping of entities across different data sources.
Especially when dealing with legal entities, the Legal Entity Identifier (LEI) can be used to uniquely identify entities.

## Installation

You can install the development version of gleif from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("m-muecke/gleif")
```

## Usage

Currently only the download of the lei mapping data is supported.

```{r}
library(gleif)

mapping <- lei_mapping("isin")
head(mapping)

records <- lei_records("001GPB6A9XPE8XJICC14", simplify = TRUE)
str(records)
```

## Related work

- [gleifr](https://github.com/Financial-Times/gleifr) - R package to support analysis of GLEIF data
